\pkg{Rgbp}: Empirical Bayesian Hierarchical Modeling

### 2013-03-09 jss/article.tex
removing newton.R

%% almost as usual
\author{Joseph Kelly\\Harvard University \And 
        Hyungsuk Tak\\Harvard University \And
        Carl Morris\\ Harvard University}
\title{\pkg{Rgbp}: Empirical Bayesian Hierarchical Modeling}

%% for pretty printing and a nice hypersummary also set:
\Plainauthor{Joseph Kelly, Hyung Suk Tak, Carl Morris} %% comma-separated
\Plaintitle{Rgbp: Empirical Bayesian Hierarchical Modeling} %% without formatting
\Shorttitle{\pkg{Rgbp}: Empirical Bayesian Hierarchical Modeling} %% a short title (if necessary)

>>>>

%% almost as usual
\author{Joseph Kelly\\Harvard University \And 
             Carl Morris\\ Harvard University\And
             Hyungsuk Tak\\Harvard University }
\title{\pkg{Rgbp}: Empirical Bayesian Hierarchical Modeling}

%% for pretty printing and a nice hypersummary also set:
\Plainauthor{Joseph Kelly, Carl Morris, Hyung Suk Tak} %% comma-separated
\Plaintitle{Rgbp: Empirical Bayesian Hierarchical Modeling} %% without formatting
\Shorttitle{\pkg{Rgbp}: Empirical Bayesian Hierarchical Modeling} %% a short title (if necessary)
